### 2016-10-26 doc/publications/plos16/plos16.tex
samlle changes to plot16.tex

The digital revolution is seeing a dramatic increase in data collected about every aspect of life~\cite{Loebbecke2015}.
These data sets are not only growing vertically, by capturing more events, but also horizontally by capturing
more information about these events.  The challenge of big and ``wide'' data is especially pronounced in the health
space where whole genome sequence (WGS) technology enables researchers to interrogate all 3 billion base pairs of the
human genome.

@@

Here we introduce \cursedforest, a Hadoop/Spark based implementation of random forests specifically designed to cater for
``big'' (many samples) and ``wide'' (many features) data sets. \cursedforest\ is capable of parallelising the split for
each node in a tree thereby handling millions of features, such as in the 1000 Genomes Project data, which consists
of approximately 2500 samples with up to 80 million variants~\cite{1KG2012}.  By also utilising Spark to read in and
manipulate the standard genomic variant format (VCF) directly, \cursedforest\ outperforms existing tools even on small
datasets where multi-threading generally performs well. 
\marginpar{``performant'' -- a person who performs, an actor or celebrant }
 \marginpar{Piotr this is your 20 trees has the important
  feature in the top 5 and 100 trees has it always as the top element, do we need to spell this out better, it should be
  a result section.}
Harnessing the virtually unlimited capability to parallelise tasks, \cursedforest\ can build a large number of trees,
which boosts the accuracy for variable importance selection~\cite{Szymczak2016}.

>>>>

The digital revolution is seeing a dramatic increase in data collected about every aspect of life~\cite{Loebbecke2015}.
These data sets are not only growing vertically, by capturing more events, but also horizontally by capturing
more information about these events.  The challenge of big and ``wide'' data is especially pronounced in the health
space where, for example, whole genome sequence (WGS) technology enables researchers to interrogate all 3 billion base pairs of the
human genome.

@@

Here we introduce \cursedforest, a Hadoop/Spark based implementation of random forests specifically designed to cater for
``big'' (many samples) and ``wide'' (many features) data sets. \cursedforest\ is capable of parallelising the split for
each node in a tree thereby handling millions of features, such as in the 1000 Genomes Project data, which consists
of approximately 2500 samples with up to 80 million variants~\cite{1KG2012}.  By also utilising Spark to read in and
manipulate the standard genomic variant format (VCF) directly, \cursedforest\ outperforms existing tools even on small
datasets where multi-threading generally performs well. 
 \marginpar{Piotr this is your 20 trees has the important
  feature in the top 5 and 100 trees has it always as the top element, do we need to spell this out better, it should be
  a result section.}
Harnessing the virtually unlimited capability to parallelise tasks, \cursedforest\ can build a large number of trees,
which boosts the accuracy for variable importance selection~\cite{Szymczak2016}.
